### 2023-06-29 bachelorthesis/41-resolution.tex
#39: Reference brief communication and minor corrections

At the beginning of this work the goal is to estimate the minimal resolution needed to run the simulation without numerical dissipation biasing the physical outcome. Numerical dissipation can therefore result to no formation of zonal flow structures, which cause a permanent turbulent state of the simulation. The goal behind this testing is to reduce \textbf{calculation time} and \textbf{costs} of the simulation. \\
Because of that, the criteria for the best resolution should be:
\begin{enumerate}
	\item[\textbf{(1)}] Subdued turbulence after \textbf{short} time periods
	\item[\textbf{(2)}] Stability for \textbf{long} time periods 
\end{enumerate}
and the following procedure will be applied for verification:
\begin{enumerate}
	\item Reduce only one number of grid points and look if criterias \textbf{(1), (2)} are satisfied
	\item Reduce to known the minimum number of grid points to verify result in general.
\end{enumerate}

>>>>

At the beginning of this work the goal is to estimate the minimal resolution needed to run the simulation without numerical dissipation biasing the physical outcome. Numerical dissipation can therefore result to no formation of zonal flow structures, which cause a permanent turbulent state of the simulation. The goal behind this testing is to reduce \textbf{calculation time} and \textbf{costs} of the simulation. \\
Because of that, the criteria for the best resolution should be:
\begin{enumerate}
	\item[\textbf{(1)}] Subdued turbulence after \textbf{short} time periods
	\item[\textbf{(2)}] Stability for \textbf{long} time periods 
\end{enumerate}
and the following procedure will be applied for verification:
\begin{enumerate}
	\item Reduce only one number of grid points and look if criteria \textbf{(1), (2)} are satisfied
	\item Reduce to the known minimum number of grid points to verify result in general.
\end{enumerate}
